%%% 1A - Lib Service Committee Offices & Committee Chairs

\subsection{Offices and Committee Chairs in organizations, committees, and task forces within the UCLA Library}

\begin{itemize}[label={}]
  \item Research Data Services Task Force, Chair, 2018
  \item Spatial Data Science Librarian Search Committee, Chair 2018-2019
\end{itemize}

%%% 1B - Membership in organizations, committees, and task forces within the UCLA Library

\subsection{Membership in organizations, committees, and task forces within the UCLA Library}

\begin{itemize}[label={}]
    \item Digital Initiatives and Information Technology Leadership Team (DIITLT), 2017 --
    \item Management Council, 2017 --
    \item Management Council, Travel Policy Committee, 2019
    \item Search Committee, Science Data Librarian; member, December 2018-April 2019
    \item TODO:CKG activity 
\end{itemize}

%%% 1C Continuing Education
\subsection{Continuing Education}

%% 1C1 Courses taken
% TODO: need to look for workshop, courses I took at conferences?
% IASSIST, ICPSR, campus courses: big data,

\begin{itemize}[label={}]
  \item Library Management Skills Institute (LMSI II): The Organization 2019. 18-21 February 2019. UC Berkeley.
  \item Core Strengths training - 4 March 2019. UCLA.
  \item Library Management Skills Institute (LMSI I): The Manager. 13-15, March 2019. USC.
  \item Crucial Conversations
\end{itemize}

% 1C2 Degrees Completed


%%% 1D Instruction & Teaching
\subsection{Instruction and Teaching}

\subsubsection{Guest lectures contributed to courses taught by others or course-integrated instruction}

\begin{itemize}[label={}]
  \item ENVIRON 188B: Sustainable LA – Grand Challenges URSP, 2 sessions, 45 students
  \item SOC SCI 402: Quantitative Data Analysis in Social Science, 2 sessions, 45 students
  \item Mellon Mays Undergraduate Fellowship Program, 2 sessions, 20 students
\end{itemize}

\subsubsection{Library-sponsored classes/workshops}

\begin{itemize}[label={}]
  \item A Hands-on Introduction to Literate Programming in R, Summer 2017, 25 learners
  \item Advanced R Book Club, 5 sessions, Summer 2019 \textbar Fall 2019,	48 learners
  \item Building interactive data applications with Shiny, Fall 2018,	10 learners
  \item Data Acquisition \& Prep in R, Spring 2018, 25 learners
  \item Data Carpentry Workshop, 1 four day workshop, Fall 2019,	36 learners
  \item Data Cleaning with R,	3 sessions,	Winter 2018 | Fall 2018 | Winter 2019, 96 learners
  \item Data Intro \& Data skills, 1 session, Winter 2019,	44 learners
  \item Data Management: File Organization,	1 session, Winter 2018,	15 learners
  \item Data Sharing Bootcamp, 1 session, Winter 2018, 19 learners
  \item Data Visualization in R, 2 sessions, Winter \& Fall 2018, 52 leaners
  \item Faculty Development Workshop: Teaching Transparent Methods of Empirical Research, 1 session, Winter 2018,	10 learners
  \item Introduction to R, 3 sessions, Winter 2018 \& 2019, 83 learners
  \item Library Carpentry Workshop, 4 two day workshops, Fall 2017 | Summer 2018 | Summer 2019, 130 learners
  \item R Programming Fundamentals,	2 sessions,	Spring 2019, 32 learners
  \item R Working Group for Master of Urban Planning, 5 sessions, Spring 2019,	67 learners
  \item Software Carpentry Workshop, 3 two day workshops, Fall 2017 | Spring 2018 | Winter 2019, 80 learners
  \item Web Scraping with Python,	1	session, Winter 2019, 13 learners
\end{itemize}

\subsubsection{UCLA (Credit) Courses taught}

\begin{itemize}[label={}]
    \item African American Studies (AF AMER) 188A: Special Courses in African American Studies. Fall 2019. 4 Units.
\end{itemize}

\subsection{Other Criterion I Activities}
\begin{itemize}[label={}]
  \item Organizer, ICPSR Data Fair 2018, Fall 2018, 5 sessions, 17 participants
  \item Organizer, Open Science Framework for Research Workflows, 1 session,	15 participants
  \item "Using Data Effectively: Carpentries Teach Tools and Best Practices", 5 presentations to the UCLA community, September, 2017,	20 participants (co-presented with Juliane Schneider, Belinda Weaver, John Chodacki, \& Todd Grappone)
  \item Put RDS taskforce
\end{itemize}
