% 2A - Memberships
\subsection{Memberships}

\begin{itemize}[label={}]
  \item Berkeley Initiative for Transparency in Social Science (BITSS): Berkeley, California, US 2017 --
  \item The Carpentries: Oakland, CA US 2016 --
  \item Center for Open Science: Charlottesville, Virginia, US 2016 --
  \item Inter-University Consortium for Political and Social Research: Ann Arbor, MI, US 2015 --
  \item International Association for Social Science Information Services and Technology, 2009 --
  \item research facilitation group RIT
\end{itemize}

% 2B - Offices, Committee Chairs, and Committee Service
\subsection{Offices, Committee Chairs, and Committee Service (in organizations listed in Section II, A)}

\begin{itemize}[label={}]
    \item Catalyst, Berkeley Initiative for Transparency in Social Science (BITSS): Berkeley, California, US 2017 --
    \item Instructor, The Carpentries: Oakland, CA US 2016 --
    \item Trainer, The Carpentries: Oakland, CA, US  2017 --
    \item Ambassador, Center for Open Science: Charlottesville, Virginia, US 2016 --
    \item Official Representative, Inter-University Consortium for Political and Social Research: Ann Arbor, MI, US 2015 --
    \item research facilitation group RIT
    \item Governance Committee, Library Carpentry, 2018-2019
    \item Curriculum Advisory Committee, Library Carpentry, 2019 --
\end{itemize}

% 2C - Conference Attendance
\subsection{Conference Attendance}

\begin{itemize}[label={}]
  \item CarpentryConnect Manchester (CCMcr19) 2019. Manchester, UK. 25-27, June 2019. https://software.ac.uk/ccmcr19.
  \item International Association for Social Science Information Services and Technology (IASSIST) 2019. Sydney, Australia. 27-31, May 2019. May
  \item UCLA Health Data Day 2019. UCLA. 9 May 2019.
\end{itemize}

% 2D Conference Participation

\subsection{Conference Participation}

\nocite{*}
\printbibliography[keyword={outlib-conf-part},title={Library-sponsored classes/workshops},heading=none]


% 2E - Teaching Outside Criterion I
\subsection{Teaching Outside Criterion I}
\begin{itemize}[label={}]
  \item Carpentries Instructor Training, 7 sessions,  October	2017, April	2017, May	2017, July	2018, October	2018, October	2018, November	2018,	164 learners
  \item Library Carpentry Workshop, 3 sessions, University of Pittsburg: May	2017, Special Library Association 2018: June, 2018, USC: August	2018,	85 learners
\end{itemize}
