%%% 1A - Lib Service Committee Offices & Committee Chairs

\subsection{Offices and Committee Chairs in organizations, committees, and task forces within the UCLA Library}

\begin{itemize}[label={},leftmargin=!,labelindent=5pt,itemindent=-15pt]
\item Chair, Management Council, October-December, 2022 
\item Founder \& Program Co-Director, UCLA Library DataSquad, June 2021 -- 
\item Chair, Data Scientist Search Committee, September 2021--December 2022
\item Chair, Emerging Technologies Librarian Search Committee, November 2019--March 2020
\item Lead, UCLA Library Carpentries Program, 2017 --
\item Director, Library Data Science Center, April 2017 --


\end{itemize}

%%% 1B - Membership in organizations, committees, and task forces within the UCLA Library

\subsection{Membership in organizations, committees, and task forces within the UCLA Library}

\begin{itemize}[label={},leftmargin=!,labelindent=5pt,itemindent=-15pt]
\item Library Task Force on Developing a Campus Digital Asset Management Task Force, 2021
\item  Library DataX Whitepaper Task Force, 2021
\item Digital Initiatives \& Information Technology Leadership Team, 2017 --
\item Management Council, 2017 --

\end{itemize}

%%% 1C Continuing Education
\subsection{Continuing Education}

%% 1C1 Courses taken
\subsubsection{Courses Taken}
\begin{itemize}[label={},leftmargin=!,labelindent=5pt,itemindent=-15pt]
  \item PSYCH 100A, Psychological Statistics, Professor James Stigler, (audited), Winter 2020
  
\end{itemize}


\subsubsection{Trainings}
% Include trainings directly related to primary job responsibilities. Do not include mandatory compliance training courses required by the University, such as Cyber Security Awareness Fundamentals.

\begin{itemize}[label=
{},leftmargin=!,labelindent=5pt,itemindent=-15pt]
  \item "Running Collaborative Online Meetings," (online), Abby Cabunoc Mayes, Mozilla Open Leaders, March 20, 2020 
  \item Big Data and AI for BioMedicine, (online) June 23, 2020 
  \item Course Kata training, summer 2020, 
\item “Career Tracks Implementation: Supervisors and Managers,” UCLA Campus Human Resources, April 29, 2021


\end{itemize}


% 1C2 Degrees Completed

%%% 1D Instruction & Teaching
\subsection{Instruction and Teaching}
%Include here instruction and teaching that is part of the candidate’s primary job responsibilities.  

\subsubsection{Guest lectures contributed to courses taught by others or course-integrated instruction}

\begin{itemize}[label={}, leftmargin=!,labelindent=5pt,itemindent=-15pt]
  \item MASS: Sustainable LA – Grand Challenges Undergraduate Research Scholars Program (URSP), 2 sessions, 45 students
  
\end{itemize}

\subsubsection{Library-sponsored classes/workshops}

\begin{itemize}[label={}, leftmargin=!,labelindent=5pt,itemindent=-15pt]
  \item Introduction to Tableau, Master of Social Science, Winter 2020
\item Software Carpentry Workshop for UCLA, 2 full-day sessions, roles: organizer \& instructor, January 15-16, 2020. (https://ucla-data-archive.github.io/2020-01-15-ucla/)
\item Library Carpentry Workshop for the UCLA iSchool (online), 8 half-day sessions, roles: organizer \& instructor, January – February 2021. (https://ucla-dataarchive.
github.io/2021-01-08-UCLA-iSchool/).
\item Software Carpentry Workshop for UCLA, 4 half-day sessions, roles: co-instructor and helper, April – May 2021. (https://ucla-data-archive.github.io/2021-04-16-
ucla/)
\item Software Carpentry Workshop for the UCs, roles: co-instructor and helper, September
10, 13, 14, 17, 20, 2021. (https://ucsdlib.github.io/2021-09-13-uc-collab/)
\item Software Carpentry Workshop for the UCs, 6 half-day sessions, role: helper, September 6-13, 2022. (https://ucsdlib.github.io/2022-09-06-carpentries-uc/)

 
\end{itemize}

\subsubsection{UCLA (Credit) Courses taught}

\begin{itemize}[label={},leftmargin=!,labelindent=5pt,itemindent=-15pt]
    \item African American Studies (AF AMER) 188A: Special Courses in African American Studies. Winter 2020. 4 Units. Instructors: Prof. Kelly Lytle Hernandez, PhD, Danielle Dupuy, PhD, Leigh Phan, Jamie Jamison, Kristian Allen \& Tim Dennis. The Data Science Center taught 50\% of the course as a technical workshop developing curriculum and graded assessments for that part of the course.
\end{itemize}

\subsection{Other Criterion I Activities}
%List significant accomplishments related to your responsibilities as reflected in the SOR other than those enumerated above, such as exhibits, work-flow development, drafting documentation, grant proposals, presentations to library staff, or contributions to library publications.

\begin{itemize}[label={},leftmargin=!,labelindent=5pt,itemindent=-15pt]
  \item Advanced R Book Club, Host, R-Ladies Los Angeles, 5 sessions, Summer 2019 \textbar Fall 2019,	48 participants
  \item  DAM Proposal 
\item DataX Whitepaper 
\item DataSquad workflow 
\end{itemize}
